---
title: |
  cageminer: mining candidate genes by integrating GWAS and gene coexpression networks
author: "Fabrício de Almeida Silva  @almeidasilvaf"
institute: "UENF, Brazil"
date: "August 2, 2021"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: ["default", "assets/venanciolab-fonts.css", "assets/venanciolab.css"]
    self_contained: false
    seal: true
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      beforeInit: "https://platform.twitter.com/widgets.js"
      navigation:
        scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE,
  fig.width = 7, fig.height = 6, fig.align='center'
)
options(htmltools.dir.version = TRUE)
```

```{r extra}
xaringanExtra::use_panelset()
xaringanExtra::use_scribble()
xaringanExtra::use_tile_view()
```

# First slide

---

class: sydney-yellow, middle, center

## Here's where you can find me:

`r icons::fontawesome("twitter")`  [@almeidasilvaf](https://twitter.com/almeidasilvaf)

`r icons::fontawesome("github")`  [almeidasilvaf](https://github.com/almeidasilvaf/)

`r icons::fontawesome("globe")`  [almeidasilvaf.github.io/home](https://almeidasilvaf.github.io/home/)

`r icons::fontawesome("envelope")`  [fabricio_almeidasilva@hotmail.com](mailto:fabricio_almeidasilva@hotmail.com)

`r icons::academicons("orcid")`  [Fabricio Almeida-Silva](https://orcid.org/0000-0002-5314-2964)


